Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-10-19 ms.Rnw
Don't save traces

  SEARCH1 = list(
    NBPF = 100,
    NP = 5000,
    SPAT_REGRESSION = 0.05,
    NREPS = 144,
    NP_EVAL = 5000,
    NREPS_EVAL = 18,
    RW_SD = chol_rw_1.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE
  )

  SEARCH2 = list(
    TOP_N = 12,
    NBPF = 100,
    NP = 5000,
    SPAT_REGRESSION = 0.05,
    NREPS = 6,
    NP_EVAL = 5000,
    NREPS_EVAL = 18,
    RW_SD = chol_rw_2.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE
  )

  SEARCH3 = list(
    TOP_N = 9,
    NBPF = 100,
    NP = 5000,
    SPAT_REGRESSION = 0.05,
    NREPS = 8,
    NP_EVAL = 5000,
    NREPS_EVAL = 18,
    RW_SD = chol_rw_3.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE,
    KEEP_LIK_MAT = TRUE
  )

>>>>

  SEARCH1 = list(
    NBPF = 100,
    NP = 5000,
    SPAT_REGRESSION = 0.05,
    NREPS = 144,
    NP_EVAL = 5000,
    NREPS_EVAL = 18,
    RW_SD = chol_rw_1.sd,
    COOLING = 0.5,
    KEEP_TRACES = FALSE
  )

  SEARCH2 = list(
    TOP_N = 12,
    NBPF = 100,
    NP = 5000,
    SPAT_REGRESSION = 0.05,
    NREPS = 6,
    NP_EVAL = 5000,
    NREPS_EVAL = 18,
    RW_SD = chol_rw_2.sd,
    COOLING = 0.5,
    KEEP_TRACES = FALSE
  )

  SEARCH3 = list(
    TOP_N = 9,
    NBPF = 100,
    NP = 5000,
    SPAT_REGRESSION = 0.05,
    NREPS = 8,
    NP_EVAL = 5000,
    NREPS_EVAL = 18,
    RW_SD = chol_rw_3.sd,
    COOLING = 0.5,
    KEEP_TRACES = FALSE,
    KEEP_LIK_MAT = TRUE
  )
